\section{Suppose that galactic supernovae obey Poissonian statistics.
The mean number of supernovae per century is 1/3.}

\begin{itemize}
    \item What is the most likely date for the next supernova?

    Poissonian statistics means we have a pdf of the form
    $P(k) = \frac{(\lambda t)^k e^{-\lambda t}}{k!}$,
    where $k$ is the number of supernova observed in time $t$ (measured in centuries),
    and $\lambda = 1/3$ is the mean number of supernovae in a century.

    To find the probability that a supernova happens at a particular time, we'll consider a small interval around that particular time and find the probability of one supernova happening inside that interval and nothing happening before.

    The probability of having one supernova after time $t$ is given by 
    $$P(k=1;t) = \lambda t e^{-\lambda t}$$.

    If we want this to be the only supernova before time $t$ we also need to consider the probability that there were no supernovae before $t$, i.e.
    $$P(k=0;t-\Delta t) = e^{-\lambda (t-\Delta t)}$$

    These two things are independent (the probability that a supernova happens in one time interval vs another) so the joint probability function is as follows:

    \begin{align*}
        P(\text{supernova in }[t-\Delta t, t]) &= P(k=0;t-\Delta t)P(k=1;t) \\
        &=  \lambda t e^{-\lambda t}e^{-\lambda (t - \Delta t)} \\
    \end{align*}

    In the limit as $\Delta t \to 0$ we get:

    \begin{align*}
        P(\text{supernova at }t) &=  \lambda t e^{-2\lambda t} \\
    \end{align*}

    This has a maximum: find it.

    \begin{align*}
        \frac{d}{dt}P(\text{supernova at }t) &=  \lambda e^{-2\lambda t} - 2\lambda^2 t e^{-2\lambda t} \\
        0 &=  \lambda e^{-2\lambda t} - 2\lambda^2 t e^{-2\lambda t} \\
        2\lambda^2 t e^{-2\lambda t} &=  \lambda e^{-2\lambda t} \\
        2\lambda t &= 1\\
        t &= \frac{1}{2\lambda}\\
        &= \frac{1}{2\frac{1}{3}}\\
        &= \frac{3}{2}\\
    \end{align*}

    So the next supernova is most likely in $1.5$ centuries.
    That's September 22, 2172. I wonder if humans will be around by then...

    \item What is the probability distribution for the length of the interval between
    now and the next galactic supernova?

    It's what we had above, the probability of the next supernova happening a time $t_0$ away from now is given by:

    $$P(t_0) = \lambda t e^{-2\lambda t_0}.$$

    (Maybe we were not supposed to derive that earlier...)

\end{itemize}


